Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-06 Papers/ViscousInstabilities/article_figure1.tex
updates

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (b) flow at t=25
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (c) flow at t=3000   
}}     
\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$. The domain is discretised with $5960$ \PN[1]{2} elements. }
\label{fem_cv_represent_a}
\end{figure}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\vspace{-.5cm}
%\hbox{\hspace{4.0cm}
%\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
%}
%\vspace{0.0cm}
%\hbox{\hspace{6.5cm} (a) Schematics of the domain
%}
%\vspace{0.25cm}
%\hbox{\hspace{4.0cm}
%\includegraphics[width=\textwidth]{./Pics1/Four_regions_coarse_MeshPermeability}
\hbox{\hspace{.8cm}
\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Sketch_5Regions.pdf}}
\vspace{-.5cm}
\hbox{\hspace{3.5cm} (a) Sketch}
\hbox{\hspace{1cm}
\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm.pdf}}
\vspace{-1.0cm}
\hbox{\hspace{3.5cm} (b) Permeability mapping ({\bf K})}
\vspace{0.0cm}
\hbox{\hspace{1cm}
\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1.pdf}}
\vspace{-1.0cm}
\hbox{\hspace{3.5cm} (c) Initial saturation distribution}}
%}
%\vspace{0.0cm}
%\hbox{\hspace{4cm} (b) Permeability distribution for coarse mesh simulation     
%}
%}     
\caption{Impact of mesh resolution on capturing flow instabilities: (a) sketch of the computational domain (dimensions in cm); (b) permeability $\left(\text{cm}^{2}\right)$, and; (c) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}. There are 13068 \PN[1]{2} element-pairs in the domain.}
\label{fig:testcase_heter_domain}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-1.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}} 
            %\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
      %\hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
\label{fig:5regions_fixedmesh}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-2.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.}
\label{fig:5regions_adaptmesh}
\end{figure}
\clearpage

@@

%%%
%%% FIGURE XXXXXX
%%%
%\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D250_meshb.pdf}
            \includegraphics[width=.5\textwidth, height=0.33\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250_edb.pdf} }
      \vspace{-0.cm}\hbox{\hspace{4.5cm}(a) fixed and adaptive mesh  }\vspace{-0.cm}
      %\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel1b.pdf}
      %      \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel2b.pdf} }
      %\vspace{-0.cm}\hbox{\hspace{1cm}(b) Darcy velocity (phase 1) \hspace{1cm}(c) Darcy velocity (phase 2) }\vspace{0.cm}
      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom1b.pdf}
             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b.pdf} }
      \vspace{-0.cm}\hbox{\hspace{4.5cm}(b) Zoom on region {\it A}  }\vspace{-0.cm}
      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom2b.pdf}
             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}
      \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}
\caption{Impact of mesh resolution on flow instabilities: capturing formation and growth of flow instabilities at fluid interfaces (t = 0.20 s) in two regions of the computational domain, {\it A} and {\it B}. Simulations were conducted with fixed (left-hand side) and adaptive meshes. }
\label{fig:5regions_AdaptZoom}
\end{figure}
%\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (b) flow at t=25
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (c) flow at t=3000   
}}     
\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$. The domain is discretised with $5960$ \PN[1]{2} elements. }
\label{fem_cv_represent_a}
\end{figure}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\vspace{-.5cm}
%\hbox{\hspace{4.0cm}
%\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
%}
%\vspace{0.0cm}
%\hbox{\hspace{6.5cm} (a) Schematics of the domain
%}
%\vspace{0.25cm}
%\hbox{\hspace{4.0cm}
%\includegraphics[width=\textwidth]{./Pics1/Four_regions_coarse_MeshPermeability}
\hbox{\hspace{.8cm}
\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Sketch_5Regions.pdf}}
\vspace{-.5cm}
\hbox{\hspace{3.5cm} (a) Sketch}
\hbox{\hspace{1cm}
\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm.pdf}}
\vspace{-1.0cm}
\hbox{\hspace{3.5cm} (b) Permeability mapping ({\bf K})}
\vspace{0.0cm}
\hbox{\hspace{1cm}
\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1.pdf}}
\vspace{-1.0cm}
\hbox{\hspace{3.5cm} (c) Initial saturation distribution}}
%}
%\vspace{0.0cm}
%\hbox{\hspace{4cm} (b) Permeability distribution for coarse mesh simulation     
%}
%}     
\caption{Impact of mesh resolution on capturing flow instabilities: (a) sketch of the computational domain (dimensions in unit-length); (b) permeability, and; (c) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}. There are 13068 \PN[1]{2} element-pairs in the domain.}
\label{fig:testcase_heter_domain}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-1.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}} 
            %\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00 \hspace{4cm} (f) t= 0.35}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10 \hspace{4cm} (g) t= 0.70}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15 \hspace{4cm} (h) t= 1.00}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20 \hspace{4cm} (i) t= 1.50}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
      %\hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 unit-time of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
\label{fig:5regions_fixedmesh}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-2.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00 \hspace{4cm} (f) t= 0.35}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10 \hspace{4cm} (g) t= 0.70}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15 \hspace{4cm} (h) t= 1.00}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20 \hspace{4cm} (i) t= 1.50}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 unit-time of numerical simulation performed with adaptive mesh and {\it VR}=10.}
\label{fig:5regions_adaptmesh}
\end{figure}
\clearpage

@@

%%%
%%% FIGURE XXXXXX
%%%
%\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D250_meshb.pdf}
            \includegraphics[width=.5\textwidth, height=0.33\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250_edb.pdf} }
      \vspace{-0.cm}\hbox{\hspace{4.5cm}(a) fixed and adaptive mesh  }\vspace{-0.cm}
      %\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel1b.pdf}
      %      \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel2b.pdf} }
      %\vspace{-0.cm}\hbox{\hspace{1cm}(b) Darcy velocity (phase 1) \hspace{1cm}(c) Darcy velocity (phase 2) }\vspace{0.cm}
      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom1b.pdf}
             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b.pdf} }
      \vspace{-0.cm}\hbox{\hspace{4.5cm}(b) Zoom on region {\it A}  }\vspace{-0.cm}
      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom2b.pdf}
             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}
      \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}
\caption{Impact of mesh resolution on flow instabilities: capturing formation and growth of flow instabilities at fluid interfaces (t = 0.20) in two regions of the computational domain, {\it A} and {\it B}. Simulations were conducted with fixed (left-hand side) and adaptive meshes. }
\label{fig:5regions_AdaptZoom}
\end{figure}
%\end{landscape}
\clearpage
